%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.3, 10 May 2020) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}

% Change the colours if you want to
\definecolor{ArchBlue}{HTML}{006acc}
\definecolor{SlateGrey}{HTML}{75747c}
\definecolor{01black}{HTML}{010101}
\colorlet{tagline}{ArchBlue}
\colorlet{heading}{ArchBlue}
\colorlet{headingrule}{ArchBlue}
\colorlet{accent}{ArchBlue}
\colorlet{emphasis}{01black}
\colorlet{body}{01black}

\renewcommand{\itemmarker}{{\small\textbullet}}
  \renewcommand{\ratingmarker}{\faCircle}

  \begin{document}
  \name{Marco A. Garcia}
  \personalinfo{%
    \email{magarcia@mail.csuchico.edu}
    \hspace{28}
    \phone{(909) 325 9532}
    \hspace{15}
    \location{Chico, CA}
    \newline
    \homepage{<in progress> marcoagarcia.com}
    \github{magarcia0}

    }

    \makecvheader

    \AtBeginEnvironment{itemize}{\small}

    \columnratio{0.6}

    \begin{paracol}{2}

      \cvsection{Experience}

      \cvevent{Webmaster}{Run For Health 5k}{December 2020 - Ongoing}{Chico, CA}
      \begin{itemize}
          \item Consulted client on a web based solution for their online presence needs.
          \item Create a modern interface for a 5k race.
          \item Maintain and update the website based on customer requests and needs
          \item https://runforhealth5k.org
      \end{itemize}

      \cvevent{Painter}{Herston Painting Inc.}{2018 - ongoing (only in summer)}{Huntsville, AL}
      \begin{itemize}
        \item Prep surfaces before application of paint (drywall repairs, putty, caulking, sanding, and masking).
        \item Maintain a clean and safe work environment.
        \item Apply different coating materials using advanced techniques (gas and electric spray machine, rollers, brushes, etc.) to appropriate surfaces (epoxy on garage floors, enamel paints on wood trim, oil paint for metals).
      \end{itemize}

      \cvevent{Painter}{First Quality Painting}{2014 - 2016}{Chino, CA}
      \begin{itemize}
        \item Cover surfaces with drop cloths or masking tape and paper to protect surfaces during painting.
        \item Fill cracks, holes, or joints with caulk, putty, plaster, or other fillers using caulking guns or putty knives.
        \item  Apply paint, enamel, or other finishes to buildings using brushes, spray guns, or rollers
        \item Remove fixtures such as pictures, door knobs, lamps, or electric switch covers prior to painting
        \item Smooth surfaces using sandpaper, scrapers, brushes, or sanding machines
      \end{itemize}
      
      \divider


      \cvsection{Education}

      \cvevent{B.S. \ in Computer Science}{Chico State University}{Aug. 2018 - May 2022}{}

      \divider

      \cvevent{A.A.\ degree in University Studies with a Math and Science Emphasis}{Chaffey Community College}{2016 - May 2018}{}

      \switchcolumn

      \cvsection{Life Philosophy}
      \begin{quote}
        \color{01black}
        ``Just keep swimming.''
      \end{quote}

      \cvsection{Strengths}
      \color{01black}
      \cvtag{Communication}
      \cvtag{Critical thinking}
      \cvtag{Patience}
      \newline

      %\divider\smallskip

      \cvsection{Technical Skills}
      \textbf{Programming Languages: }
      \newline
      \cvtag{C++}
      \cvtag{C}
      \cvtag{Python}
      \newline
      \textbf{Database/Platforms:}
      \newline
      \cvtag{MySQL} 
      \cvtag{AWS}
      \newline
      \cvtag{GIT}
      \newline
      \cvsection{Other Skills}
      \cvtag{IBM Quantum Circuit Builder}

      %\cvsection{References}

    \end{paracol}
    \cvsection{Extra Curricular}

    \cvevent{Chico State Crew}{CSU Chico}{2019 - 2020}{Chico, CA}
    \begin{itemize}
      \item Sweep rower on port side.
      \item Stroke seat.
    \end{itemize}

  \end{document}

